Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-03-23 Paper.tex
Make sure only one version of the protocol is described

\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \begin{cases}
\boldsymbol{\sigma} & \text{if} \quad \boldsymbol{\sigma}^{**} = \varnothing \\
\boldsymbol{\sigma}^{**} & \text{otherwise}
\end{cases} \\
(\boldsymbol{\sigma}^{**}, g', \mathbf{s}, \mathbf{o}) & \equiv & \begin{cases}
\Xi_{\mathtt{ECREC}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 1 \\
\Xi_{\mathtt{SHA256}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 2 \\
\Xi_{\mathtt{RIP160}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 3 \\
\Xi_{\mathtt{ID}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 4 \\
\Xi_{\mathtt{ADD}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 5 \\
\Xi_{\mathtt{SUB}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 6 \\
\Xi_{\mathtt{MUL}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 7 \\
\Xi_{\mathtt{DIV}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 8 \\
\Xi_{\mathtt{EXPMOD}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 9 \\
\Xi(\boldsymbol{\sigma}_1, g, I) & \text{otherwise} \end{cases} \\
I_a & \equiv & r \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & \tilde{v} \\
I_e & \equiv & e \\
\text{Let} \; \mathtt{\tiny KEC}(I_\mathbf{b}) & = & \boldsymbol{\sigma}[c]_c
\end{eqnarray}

@@

The fourth contract, the identity function $\Xi_{\mathtt{ID}}$ simply defines the output as the input:
\begin{eqnarray}
\Xi_{\mathtt{ID}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_r &=& 15 + 3\Big\lceil \dfrac{|I_\mathbf{d}|}{32} \Big\rceil\\
\mathbf{o} &=& I_\mathbf{d}
\end{eqnarray}

The fifth contract performs arbitrary-precision addition on non-negative integers.
The first word in the input specifies the number of bytes that the first non-negative integer $X$ occupies.
The result is represented in the smallest possible number of bytes.  The first byte in the output is never zero.

\begin{eqnarray}
\Xi_{\mathtt{ADD}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{except:}\\
\Xi_{\mathtt{ADD}}(\boldsymbol{\sigma}, g, I) &\equiv& (\varnothing, 0, A^0, ()) \quad \text{if} \quad |I_\mathbf{d}| - 32 <  I_\mathbf{d}[0..31] \\
g_r &=& G_{addsubbase} + G_{arithword} \Big\lceil \dfrac{|I_\mathbf{d}|}{32} \Big\rceil \\
\mathbf{o} &=& (X + Y) \in \mathbb{B}_\ell \\
X &=& I_\mathbf{d}[32..(32 + I_\mathbf{d}[0..31] - 1)] \\
Y &=& I_\mathbf{d}[(32 + I_\mathbf{d}[0..31])..(|I_\mathbf{d}| - 1)] \\
\ell &=&
\begin{cases}
0 &\text{if}\, X = Y = 0 \\
\lfloor \log_8(X + Y) \rfloor + 1 & \text{otherwise}
\end{cases}
\end{eqnarray}

The sixth contract performs arbitrary-precision subtraction on non-negative integers.  This is similar to the addition.  The subtraction contract halts exceptionally if the result would be negative.

\begin{eqnarray}
\Xi_{\mathtt{SUB}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{except:}\\
\Xi_{\mathtt{SUB}}(\boldsymbol{\sigma}, g, I) &\equiv& (\varnothing, 0, A^0, ()) \quad \text{if} \quad |I_\mathbf{d}| - 32 <  I_\mathbf{d}[0..31] \\
\Xi_{\mathtt{SUB}}(\boldsymbol{\sigma}, g, I) &\equiv& (\varnothing, 0, A^0, ()) \quad \text{if} \quad X < Y \\
g_r &=& G_{addsubbase} + G_{arithword} \Big\lceil \dfrac{|I_\mathbf{d}|}{32} \Big\rceil \\
\mathbf{o} &=& (X - Y) \in \mathbb{B}_\ell \\
X &=& I_\mathbf{d}[32..(32 + I_\mathbf{d}[0..31] - 1)] \\
Y &=& I_\mathbf{d}[(32 + I_\mathbf{d}[0..31])..(|I_\mathbf{d}| - 1)] \\
\ell &=&
\begin{cases}
0 &\text{if}\ X = Y \\
\lfloor \log_8(X - Y) \rfloor + 1 & \text{otherwise}
\end{cases}
\end{eqnarray}

The seventh contract performs arbitrary-precision multiplication on non-negative integers.  The input format is the same as that of the addition contract.

\begin{eqnarray}
\Xi_{\mathtt{MUL}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{except:}\\
\Xi_{\mathtt{MUL}}(\boldsymbol{\sigma}, g, I) &\equiv& (\varnothing, 0, A^0, ()) \quad \text{if} \quad |I_\mathbf{d}| - 32 <  I_\mathbf{d}[0..31] \\
g_r &=& G_{muldivbase} + G_{arithword} \Big\lceil \dfrac{|I_\mathbf{d}|}{32} \Big\rceil + \ell_X \ell_Y / G_{quaddivisor} \\
\mathbf{o} &=& (X \times Y) \in \mathbb{B}_\ell \\
X &=& I_\mathbf{d}[32..(32 + I_\mathbf{d}[0..31] - 1)] \\
\ell_X &=& I_\mathbf{d}[0..31] \\
Y &=& I_\mathbf{d}[(32 + I_\mathbf{d}[0..31])..(|I_\mathbf{d}| - 1)] \\
\ell_Y &=& |I_\mathbf{d}| - 32 - \ell_X \\
\ell &=&
\begin{cases}
0 &\text{if}\ X = 0 \ \vee\  Y = 0 \\
\lfloor \log_8(X \times Y) \rfloor + 1 & \text{otherwise}
\end{cases}
\end{eqnarray}

The eigth contract performs arbitrary-precision division on non-negative integers.  The definition is similar to that of the multiplication contract.

\begin{eqnarray}
\Xi_{\mathtt{DIV}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{except:}\\
\Xi_{\mathtt{DIV}}(\boldsymbol{\sigma}, g, I) &\equiv& (\varnothing, 0, A^0, ()) \quad \text{if} \quad |I_\mathbf{d}| - 32 <  I_\mathbf{d}[0..31] \\
g_r &=& G_{muldivbase} + G_{arithword} \Big\lceil \dfrac{|I_\mathbf{d}|}{32} \Big\rceil + \ell_X \ell_Y / G_{quaddivisor} \\
\mathbf{o} &=&
\begin{cases}
 () & \text{if} \  Y = 0 \\
 \Big\lfloor \dfrac X Y \Big\rfloor \in \mathbb{B}_\ell & \text{otherwise}
\end{cases} \\
X &=& I_\mathbf{d}[32..(32 + I_\mathbf{d}[0..31] - 1)] \\
\ell_X &=& I_\mathbf{d}[0..31] \\
Y &=& I_\mathbf{d}[(32 + I_\mathbf{d}[0..31])..(|I_\mathbf{d}| - 1)] \\
\ell_Y &=& |I_\mathbf{d}| - 32 - \ell_X \\
\ell &=&
\begin{cases}
0 &\text{if}\ Y = 0 \ \vee \ \Big\lfloor \dfrac X Y \Big\rfloor = 0 \\
\lfloor \log_8(\Big\lfloor \dfrac X Y \Big\rfloor) \rfloor + 1 & \text{otherwise}
\end{cases}
\end{eqnarray}

The ninth contract performs arbitrary-precision exponentiation under modulo.  Here, $0 ^ 0$ is taken to be one.
\begin{eqnarray}
\Xi_{\mathtt{EXPMOD}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{except:}\\
\ell_B &=& I_\mathbf{d}[0..31] \\
\ell_E &=& I_\mathbf{d}[32..63] \\
B &=& I_\mathbf{d}[64..(63 + \ell_B)] \\
E &=& I_\mathbf{d}[(64 + \ell_B)..(63 + \ell_B + \ell_E)] \\
M &=& I_\mathbf{d}[(64 + \ell_B + \ell_E)..(|I_\mathbf{d}| - 1)] \\
\Xi_{\mathtt{EXPMOD}}(\boldsymbol{\sigma}, g, I) &\equiv& (\varnothing, 0, A^0, ()) \quad \text{if} \quad |I_\mathbf{d}| < 64 + \ell_B + \ell_E \\
g_r &=& G_{modexpbase} + G_{arithword} \Big\lceil \dfrac{|I_\mathbf{d}|}{32} \Big\rceil + |M|^2 |E| / G_{quaddivisor} \\
\mathbf{o} &=&
\begin{cases}
 () & \text{if} \  M = 0 \\
 B ^ E \bmod M \in \mathbb{B}_\ell & \text{otherwise}
\end{cases} \\
\ell &=&
\begin{cases}
0 &\text{if}\ M = 0 \quad \vee \quad {B ^ E} \bmod M = 0 \\
\lfloor \log_8(B ^ E \bmod M) \rfloor + 1 & \text{otherwise}
\end{cases}
\end{eqnarray}

>>>>

\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \begin{cases}
\boldsymbol{\sigma} & \text{if} \quad \boldsymbol{\sigma}^{**} = \varnothing \\
\boldsymbol{\sigma}^{**} & \text{otherwise}
\end{cases} \\
g' & \equiv & \begin{cases}
0 & \text{if} \quad \boldsymbol{\sigma}^{**} = \varnothing \\
g^{**} & \text{otherwise}
\end{cases} \\
(\boldsymbol{\sigma}^{**}, g^{**}, \mathbf{s}, \mathbf{o}) & \equiv & \begin{cases}
\Xi_{\mathtt{ECREC}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 1 \\
\Xi_{\mathtt{SHA256}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 2 \\
\Xi_{\mathtt{RIP160}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 3 \\
\Xi_{\mathtt{ID}}(\boldsymbol{\sigma}_1, g, I) & \text{if} \quad r = 4 \\
\Xi(\boldsymbol{\sigma}_1, g, I) & \text{otherwise} \end{cases} \\
I_a & \equiv & r \\
I_o & \equiv & o \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & \mathbf{d} \\
I_s & \equiv & s \\
I_v & \equiv & \tilde{v} \\
I_e & \equiv & e \\
\text{Let} \; \mathtt{\tiny KEC}(I_\mathbf{b}) & = & \boldsymbol{\sigma}[c]_c
\end{eqnarray}

@@

Finally, the fourth contract, the identity function $\Xi_{\mathtt{ID}}$ simply defines the output as the input:
\begin{eqnarray}
\Xi_{\mathtt{ID}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_r &=& 15 + 3\Big\lceil \dfrac{|I_\mathbf{d}|}{32} \Big\rceil\\
\mathbf{o} &=& I_\mathbf{d}
\end{eqnarray}
